Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex

more features (this is the hardest, and most manual part, may require
domain-specific knowledge, but not necessariyly, e.g. microbenchmarking)
* features derived from micro-benchmarking \citep{wong2010demystifying}
* features derived from performance limiter analysis \citep{micikevicius2010analysis}
* more instrumentation
* more data-layout
* more threading strategies to lower latency
(finding a good representation is key, again...)

online distributed auto-tuning with learning, especially w/ HT-based
experiments \cite{HT} our method is indeed very well suited for parallel
explorating of multiple configurations for learning (in a cluster, e.g. in HT
context) this may get us \emph{more} than linear speed ups for better accuracy,
especially when more features will be present (see above)

interpret the learned model and confront the performance against theoreticial
(or approximated) models of mem/com/compute, arithmetic intensity, etc. to
understand performance limiters, the hardware, etc.

>>>>

While the present work serves as a basic demonstration of the value of using machine learning models to predict optimal implementation parameters, there are many avenues for taking these ideas further. A natural route to extend of our current approach is to include more features as inputs to the predictive model.  In addition to further instrumentation of the kernel in question, input features could include a much broader range of hardware-related information, from more detailed information about device capabilities to micro-benchmarks  \citep{wong2010demystifying}, and results from performance limiter analyses \citep{micikevicius2010analysis}. Such additional features would increase the predictive model's ability to adapt to a wide range of different kinds of hardware, including new devices not available at the time of kernel creation.

Another potentially interesting avenue of research is in interpreting the model learned by predictive auto-tuning.  While traditional model-based auto-tuning approaches by design assume a given model, and empirical auto-tuning approaches are completely model free, the predictive approach described here \emph{generates} a model from performance data.  Because this generated model can be interrogated by a variety of means, a significant opportunity exists to learn about the factors that drive the performance of a given kernel.  These insights can be used to further guide the development and instrumentation of the kernel, potentially yielding even greater gains.

% more features (this is the hardest, and most manual part, may require
% domain-specific knowledge, but not necessariyly, e.g. microbenchmarking)
% * features derived from micro-benchmarking \citep{wong2010demystifying}
% * features derived from performance limiter analysis \citep{micikevicius2010analysis}

% DDC: these aren't terribly general / interesting to a broad audience

% * more instrumentation
% * more data-layout
% * more threading strategies to lower latency
% (finding a good representation is key, again...)
% 
% online distributed auto-tuning with learning, especially w/ HT-based
% experiments \cite{HT} our method is indeed very well suited for parallel
% explorating of multiple configurations for learning (in a cluster, e.g. in HT
% context) this may get us \emph{more} than linear speed ups for better accuracy,
% especially when more features will be present (see above)
% 
% interpret the learned model and confront the performance against theoreticial
% (or approximated) models of mem/com/compute, arithmetic intensity, etc. to
% understand performance limiters, the hardware, etc.
